Toward a More Accessible and Reproducible ISLS Conference Proceedings Paper: A Practical Workshop Using Cutting-Edge Tools

### 2021-01-09 paper_contents.tex
Change markdown into latex

A number of theoretical ideas are relevant to the focus of this workshop;
the first is reproducibility. Scholars have argued that reproducibility should
be a *minimal* standard as a means of combating the *replicability crisis* [@peng11, @hedges18]. 
Reproducibility typically involves using tools and software, such as the R 
statistical software and programming language [@rcoreteam2020]; through the use of 
R, each of the steps in an analysis, from reading and processing raw data to creating
models and visualizations of data, can be written in such a way that an analysis
may be reproduced---by the analyst or others. Through the use of tools such as R, 
analyses, especially but not only those that are quantitative in nature, are more
open and transparent, and the likelihood of reproducibility and trustworthiness
of research can be increased. Especially in education, reproducibility is 
important [@vanderzee2018], but has been emphasized less than in conversations about 
research practice than in closely-related fields, including computer science and psychology.

The second relevant theoretical idea is accessibility. Accessibility refers to 
the state of digital technologies, including web-based materials, not having barriers
to their use. Accessibility is particularly relevant to sharing scholarly work [seo2019arow];
a number of tools have made writing not only text but also code including the typesetting 
language LaTeX and R Markdown,  the latter of which can allow for written text and analytic 
R code to be woven together in a way that can make code more easy to understand [@knuth1984].

>>>>

A number of theoretical ideas are relevant to the focus of this workshop;
the first is reproducibility. Scholars have argued that reproducibility should
be a \textit{minimal} standard as a means of combating the \textit{replicability crisis} \parencite{peng11, hedges18}. 
Reproducibility typically involves using tools and software, such as the R 
statistical software and programming language \parencite{rcoreteam2020}; through the use of 
R, each of the steps in an analysis, from reading and processing raw data to creating
models and visualizations of data, can be written in such a way that an analysis
may be reproduced---by the analyst or others. Through the use of tools such as R, 
analyses, especially but not only those that are quantitative in nature, are more
open and transparent, and the likelihood of reproducibility and trustworthiness
of research can be increased. Especially in education, reproducibility is 
important \parencite{vanderzee2018}, but has been emphasized less than in conversations about 
research practice than in closely-related fields, including computer science and psychology.

The second relevant theoretical idea is accessibility. Accessibility refers to 
the state of digital technologies, including web-based materials, not having barriers
to their use. Accessibility is particularly relevant to sharing scholarly work \parencite{seo2019arow};
a number of tools have made writing not only text but also code including the typesetting 
language LaTeX and R Markdown,  the latter of which can allow for written text and analytic 
R code to be woven together in a way that can make code more easy to understand \parencite{knuth1984}.
